Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
up

Since {\sc $t$-liveness} is undecidable, from Proposition~\ref{reductions},  we deduce that {\sc State-resilience} is undecidable  for reset-VASS, which are WSTS with strong compatibility. Hence {\sc State-resilience} is undecidable  for WSTS with strong upward-compatibility.

@@

 \begin{center}
	\begin{figure}
\includegraphics[width=0.75\textwidth]{FigurePN}
\caption{Construction of $N_2$ from $N_1$. Places are represented using circles, transitions are represented using lines. Arcs are represented by $\rightarrow$ and reset-arcs by $\arrowcircle$. Note that since the construction of $N_2$ from $N_1$ do not add new reset-arcs, the only reset-arcs in $N_2$ are the ones inherited from $N_1$.}
	\end{figure}
\end{center}

>>>>

Since {\sc $t$-liveness} is undecidable, from Proposition~\ref{reductions},  we deduce that {\sc State-resilience} is undecidable  for reset-VASS, which are WSTS with strong upward-compatibility. Hence {\sc State-resilience} is undecidable  for WSTS with strong upward-compatibility.

@@

 \begin{center}
	\begin{figure}
\includegraphics[width=0.75\textwidth]{FigurePN}
\caption{Construction of $N_2$ from $N_1$.}
	\end{figure}
\end{center}
